Einstein's gravity from a polynomial affine model

### 2016-05-03 AffGR-PRD.tex
Several modifications. Comments about future changes

The equation for the Curtright field when the scalar field is turned on is (without lost of generality we fixed the coefficient $C_1 = 1$)
\begin{equation*}
  \nabla_{[\sigma} R_{\rho]\mu}{}^{\mu}{}_\nu - {C_2} \nabla_\nu  R_{\rho\sigma}{}^{\mu}{}_\mu - \alpha \nabla_{[\sigma} \Big( \partial_{\rho]}\phi \partial_\nu\phi \Big) = 0,
\end{equation*}
which under our considerations simplifies to 
\begin{equation}
  \nabla_{[\sigma} R_{\rho]\nu} - \alpha \nabla_{[\sigma} \Big( \partial_{\rho]}\phi \partial_\nu\phi \Big) = 0.
  \label{SimpleEOMwS}
\end{equation}
%% when the connection is the Levi-Civita one.
In that case, we find a particular solution of Eq.~\eqref{SimpleEOMwS},%% \hl{JZ: What if non-LC connection?}
\begin{equation*}
  R_{\mu\nu} - \alpha \pa{\mu} \phi \pa{\nu} \phi = \Lambda g_{\mu\nu},
\end{equation*}
that can be written in the more conventional form~\footnote{Notice that $\alpha$ is the gravitational coupling constant, which in Einstein--Hilbert gravity is $G_N$.}
\begin{equation}
  R_{\mu\nu} - \frac{1}{2} g_{\mu\nu} R + \Lambda g_{\mu\nu} = \alpha \Big( \pa{\mu} \phi \pa{\nu} \phi - \frac{1}{2} g_{\mu\nu} \big( \partial\phi \big)^2 \Big).
\end{equation}
Additionally, the second Bianchi identity imposes
\begin{equation}
  \nabla^\mu \pa{\mu} \phi = 0.
\end{equation}
%% \hl{JZ: Esto muestra que la teoria contiene a R.G. com ocaso particular, pero tiene probablemente mucho mas. Que es lo extra?}
This condition is, in the sense argued in Ref.~\cite{Bekenstein:2014uwa}, the equation of motion for the scalar field. Notice that, the Euler--Lagrange equation of motion for the scalar field yields no information after taking the vanishing torsion \emph{truncation}.

@@

A first step toward the analysis of renormalizability of the model should be the computation of the free propagators of the model around a given background. The choice of background will necessarily be taken in order to simplify the computations.  Our first task is to expand up to second order in the fields around a flat background. Under these assumptions, and using the notation of Eqs.~\eqref{GammaExp}, the relevant part of the action~\eqref{4dfull} is

@@

    S[\gamma,t,a] =

@@

      C_1 \partial_{\mu}\gamma^{\mu}{}_{\rho\nu} \partial_\sigma t^{\nu\rho\sigma}
      +2 C_2 \partial_{\mu}\gamma^{\rho}{}_{\nu\rho} \partial_\sigma t^{\sigma\mu\nu}
      + E_1 \partial_{(\rho}t^{\rho\mu\nu}\partial_{\sigma)}t^{\sigma\lambda\kappa}\epsilon_{\mu\nu\lambda\kappa}
      + E_2 \partial_{(\lambda} t^{\lambda\mu\nu}\partial_{\mu)} a_\nu

@@

@@

In momentum space, the second order perturbation is

@@

  \label{4dflat}
  S =
  \int\dn{4}{p}\bigg[
    C_1 p_{\mu} p_\sigma\tilde\gamma^{\mu}{}_{\rho\nu}^* \tilde t^{\nu\rho\sigma}
    + 2 C_2 p_{\mu} p_\sigma\tilde\gamma^{\rho}{}_{\nu\rho}^* \tilde t^{\sigma\mu\nu}
    + E_1 p_{\rho} p_{\sigma} \tilde t^{\rho\mu\nu}{}^*\tilde t^{\sigma\lambda\kappa} \epsilon_{\mu\nu\lambda\kappa}
    + E_2 p_{\lambda} p_{\mu} \tilde t^{\lambda\mu\nu}{}^* \tilde a_\nu

@@

Longitudinal and transverse projectors can be introduced in order to decompose the action and specify in a more standard fashion the dynamics of Eq.~\eqref{4dflat}. This can be done since we have the metric $\eta_{\mu\nu}$ compatible with the connection and $p^\mu = \eta^{\mu\nu}p_\nu$. We define the projector into logitudinal vectors $P_{\texttt{L}}{}^\mu_\nu = \tfrac{1}{p^2}p^\mu p_\nu $, such that $$A_{\texttt{L}\mu} = P_{\texttt{L}}{}^\nu_\mu \, A_\nu = A_{\texttt{L}}{}p_{\mu},$$ where $A_{\texttt{L}}=\tfrac{1}{p^2} p^\mu A_\mu$. Similarly, $P_\perp{}^\mu_\nu=\delta^\mu_\nu -P_{\texttt{L}}{}^\mu_\nu$ defines the projector into transverse vectors, i.e., $A_{\perp \mu}=P_{\perp}{}_\mu^\nu A_\nu$. Thus,

@@

  \label{transversea}
  \tilde a_\nu=a_\perp{}_{\nu}+a_{\texttt{L}} p_\nu,
  \label{transverset}
  \tilde t^{\lambda\mu\nu}=\frac{1}{p}\epsilon^{\mu\nu\kappa\rho}p_\rho t_\perp^{\lambda}{}_\kappa+\frac{1}{p^2}p^\lambda\epsilon^{\mu\nu\kappa\rho}p_\rho t_{\texttt{a}\kappa}-\frac{2}{p^2}p^{[\mu}\epsilon^{\nu]\lambda\kappa\rho}p_\rho t_{\texttt{a}\kappa}+\frac{2}{p}p^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+\frac{2}{p^2}p^\lambda p^{[\mu} t_{\texttt{v}}^{\nu]},
  \label{transversegamma}
  \tilde \gamma^{\lambda}{}_{\mu\nu}=\gamma_\perp^{\lambda}{}_{\mu\nu}+\frac{1}{p}p^\lambda \gamma_{\texttt{s}}{}_{\mu\nu}+\frac{2}{p}p_{(\mu} \gamma^\lambda{}_{\nu)}+\frac{2}{p^2}p^\lambda p_{(\mu} \gamma_{\texttt{v}}{}_{\nu)}+ \frac{1}{p^2}p_{\mu} p_{\nu} \gamma'_{\texttt{v}}{}^\lambda+\frac{1}{p^3}p^\lambda p_{\mu} p_{\nu} \gamma_{\texttt{L}},
where all the indices are transverse except those of the momentum $p_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the subindices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation. In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless. Additionally, we could separate the fields into irreducible representations by projecting them into their traceless part and other lower dimensional tensor representations. In the meanwhile we shall not do this expansion.
  Using Eqs.~\eqref{transversea}, \eqref{transverset} and~\eqref{transversegamma}, the action~\eqref{4dflat} is then rewritten
    \label{4dtransverse}
    S =
    \int\dn{4}{p}p^2
    \bigg[
      2C_1 \hat{p}_\mu \hat{p}_\sigma\Big(\gamma_\perp^{\mu}{}_{\rho\nu}+\hat{p}^\mu \gamma_{\texttt{s}}{}_{\rho\nu}+2\hat{p}_{(\rho} \gamma^\mu{}_{\nu)}+2\hat{p}^\mu \hat{p}_{(\rho} \gamma_{\texttt{v}}{}_{\nu)}+ \hat{p}_{\rho} \hat{p}_{\nu} \gamma'_{\texttt{v}}{}^\mu+\hat{p}^\mu \hat{p}_{\rho} \hat{p}_{\nu} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\rho\sigma\delta\eta}\hat{p}_\eta t_\perp^{\nu}{}_\delta+\hat{p}^\nu t_{\texttt{a}}^{\rho\sigma}-2\hat{p}^{[\rho} t_{\texttt{a}}^{\sigma]\nu}+2\hat{p}^{[\rho} t_{\texttt{s}}^{\sigma]\nu}+2\hat{p}^\nu \hat{p}^{[\rho} t_{\texttt{v}}^{\sigma]}\Big)
      +2C_2 \hat{p}_{\mu} \hat{p}_\sigma\Big(\gamma_\perp^{\rho}{}_{\nu\rho}+\hat{p}^\rho \gamma_{\texttt{s}}{}_{\nu\rho}+2\hat{p}_{(\nu} \gamma^\rho{}_{\rho)}+2\hat{p}^\rho \hat{p}_{(\nu} \gamma_{\texttt{v}}{}_{\rho)}+\hat{p}_{\nu} \hat{p}_{\rho} \gamma'_{\texttt{v}}{}^\rho +\hat{p}^\rho \hat{p}_{\nu} \hat{p}_{\rho} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\kappa+\hat{p}^\sigma t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\sigma}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\sigma}+2\hat{p}^\sigma \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)
      +E_1 \hat{p}_{\rho} \hat{p}_{\sigma}\Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\rho}{}_\kappa+\hat{p}^\rho t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{\mu} t_{\texttt{a}}^{\nu\rho}+2\hat{p}^{\mu} t_{\texttt{s}}^{\nu\rho}+2\hat{p}^\rho \hat{p}^{\mu} t_{\texttt{v}}^{\nu}\Big)^*\Big(\epsilon^{\lambda\kappa\delta\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\delta+\hat{p}^\sigma t_{\texttt{a}}^{\lambda\kappa}-2\hat{p}^{\lambda} t_{\texttt{a}}^{\kappa\sigma}+2\hat{p}^{\lambda} t_{\texttt{s}}^{\kappa\sigma}+2\hat{p}^\sigma \hat{p}^{\lambda} t_{\texttt{v}}^{\kappa}\Big)\epsilon_{\mu\nu\lambda\kappa}
      +E_2 \hat{p}_{\lambda} \hat{p}_{\mu} \Big(\epsilon^{\mu\nu\kappa\rho}\hat{p}_\rho t_\perp^{\lambda}{}_\kappa+\hat{p}^\lambda t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\lambda}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+2\hat{p}^\lambda \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)^*\Big(a_\perp{}_\nu+\hat{p}_\nu a_{\texttt{L}}\Big)

@@

simplifiying
  \label{WithGhosts}
  S=\int d^4p\Bigg[-2C_1 p^2\gamma_{\texttt{s}\mu\nu}^*t_{\texttt{s}}^{\mu\nu}
    +p^2\Big((-2C_1+2C_2)\gamma_{\texttt{v}\mu}+2C_2\gamma_{\perp\mu\nu}^\nu
    +8E_1t_{\texttt{a}\mu}+E_2a_{\perp\mu}\Big)^*t_{\texttt{v}}^\mu
    \Bigg]

@@

In this paper we have shown that the \emph{purely affine gravity} presented in Ref.~\cite{Skirzewski:2014eta} is the most general (polynomial) model for an affine theory of gravity, see the Appendix~\ref{sec:ld}, consistent with invariance under diffeomorphisms. The action in Eq.~\eqref{4dfull}, is parametrized by a nineteen-dimensional moduli space---after the boundary and topological terms have been dropped---, which in some sense made us wonder about a possible \emph{duality} between this model and the one proposed in Ref.~\cite{Pagani:2015ema}, even though the last one possesses a metric field.
%% (boundary condition, topological terms, ...)

>>>>

The equation for the Curtright field when the scalar field is turned on is (without lost of generality we fixed the coefficient $C_1 = 1$)
\begin{equation*}
  \nabla_{[\sigma} R_{\rho]\mu}{}^{\mu}{}_\nu - {C_2} \nabla_\nu  R_{\rho\sigma}{}^{\mu}{}_\mu - \alpha \nabla_{[\sigma} \Big( \partial_{\rho]}\phi \partial_\nu\phi \Big) = 0,
\end{equation*}
which under our considerations simplifies to 
\begin{equation}
  \nabla_{[\sigma} R_{\rho]\nu} - \alpha \nabla_{[\sigma} \Big( \partial_{\rho]}\phi \partial_\nu\phi \Big) = 0.
  \label{SimpleEOMwS}
\end{equation}
%% when the connection is the Levi-Civita one.
In that case, we find a particular solution of Eq.~\eqref{SimpleEOMwS},%% \hl{JZ: What if non-LC connection?}
\begin{equation*}
  R_{\mu\nu} - \alpha \pa{\mu} \phi \pa{\nu} \phi = \Lambda g_{\mu\nu},
\end{equation*}
that can be written in the more conventional form~\footnote{We have used a suggestive notation by denoting with $g_{\mu\nu}$ a covariantly constant, invertible, and symmetric two-tensor. Notice that $\alpha$ is the gravitational coupling constant, which in Einstein--Hilbert gravity is proportional to $G_N$.}
\begin{equation}
  R_{\mu\nu} - \frac{1}{2} g_{\mu\nu} R + \Lambda g_{\mu\nu} = \alpha \Big( \pa{\mu} \phi \pa{\nu} \phi - \frac{1}{2} g_{\mu\nu} \big( \partial\phi \big)^2 \Big).
\end{equation}
Additionally, the second Bianchi identity imposes
\begin{equation}
  \nabla^\mu \pa{\mu} \phi = 0.
\end{equation}
%% \hl{JZ: Esto muestra que la teoria contiene a R.G. com ocaso particular, pero tiene probablemente mucho mas. Que es lo extra?}
This condition is, in the sense argued in Ref.~\cite{Bekenstein:2014uwa}, the equation of motion for the scalar field. Notice that, the Euler--Lagrange equation of motion for the scalar field yields no information after taking the vanishing torsion \emph{truncation}.

@@

A step toward the analysis of renormalizability of the model should be the computation of the free propagators of the model around a given background. The choice of background will necessarily in order to simplify the computations.  Our first task is to expand up to second order in the fields around a maximally symmetric Riemannian background. Maximally symmetric spaces possess remarkably simple curvature tensors~\cite{weinberg1972gravitation},
  R_{\mu\nu}{}^\lambda{}_\rho = {K} \Big( g_{\nu\rho} \delta^\lambda_\mu - g_{\mu\rho} \delta^\lambda_\nu \Big),
and the Einstein's field equations in vacuum
  R_{\mu\nu} = \Lambda \, g_{\mu\nu},
require that $K = \frac{\Lambda}{3}$. 
%% Additionally, 
Therefore, in notation of Eqs.~\eqref{GammaExp} we have that $A = T = 0$, and the contribution due to the torsion (and non-metricity) enters as a perturbative effect. Thus, most terms in the action~\eqref{4dfull} do not contribute to the propagator analysis. Additionally, the first order perturbation of the curvature tensor is
  R_{\mu\nu}{}^\lambda{}_\rho = \frac{\Lambda}{3}\,   {\delta}^{\lambda}_{\mu} {g}_{\rho \nu} - \frac{\Lambda}{3}\,   {\delta}^{\lambda}_{\nu} {g}_{\rho \mu} + {\nabla}_{\mu}{{\gamma}^{\lambda}\,_{\rho \nu}}\,  - {\nabla}_{\nu}{{\gamma}^{\lambda}\,_{\rho \mu}}.
Under these assumptions, the relevant terms of the action~\eqref{4dfull} are those accompanied by the couplings $B_i$, $C_i$ and $E_i$, and the second order perturbation of the action yields

@@

    S^{(2)}[\gamma,t,a] =

@@

      C_1 \big( - \Lambda {\nabla}_{\alpha}{{t}^{\beta \alpha \gamma}}\,  {g}_{\beta \gamma} - \Lambda {\gamma}^{\alpha}\,_{\beta \delta} {g}_{\alpha \gamma} {t}^{\beta \delta \gamma} + {\nabla}_{\alpha}{{\gamma}^{\alpha}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\beta \delta \gamma}}\,  - {\nabla}_{\alpha}{{\gamma}^{\beta}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\delta \alpha \gamma}}\, \big)
      + 2\, C_2 {\nabla}_{\alpha}{{\gamma}^{\beta}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\gamma \alpha \delta}}\,
      + E_1 {\epsilon}_{\alpha \beta \delta \eta} {\nabla}_{\gamma}{{t}^{\gamma \alpha \beta}}\,  {\nabla}_{\lambda}{{t}^{\lambda \delta \eta}}\,
      + E_2 \big({\nabla}_{\alpha}{{a}_{\beta}}\,  {\nabla}_{\gamma}{{t}^{\gamma \alpha \beta}}\,  - {\nabla}_{\alpha}{{a}_{\beta}}\,  {\nabla}_{\gamma}{{t}^{\alpha \beta \gamma}}\, \big)
      + \Big(B_1 + \frac{1}{3}\, B_2 \Big) \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {g}_{\eta \lambda} {t}^{\eta \alpha \beta} {t}^{\lambda \gamma \delta}
      + \Big( - B_3 + \frac{2}{3}\, B_4 \Big) \Lambda {a}_{\alpha} {g}_{\beta \gamma} {t}^{\beta \alpha \gamma}

@@

    \label{4dmax}

@@

%% In momentum space, the second order perturbation is
%% \begin{dmath}[compact, spread=2pt]
%%   \label{4dflat}
%%   S =
%%   \int\dn{4}{p}\bigg[
%%     C_1 p_{\mu} p_\sigma\tilde\gamma^{\mu}{}_{\rho\nu}^* \tilde t^{\nu\rho\sigma}
%%     + 2 C_2 p_{\mu} p_\sigma\tilde\gamma^{\rho}{}_{\nu\rho}^* \tilde t^{\sigma\mu\nu}
%%     + E_1 p_{\rho} p_{\sigma} \tilde t^{\rho\mu\nu}{}^*\tilde t^{\sigma\lambda\kappa} \epsilon_{\mu\nu\lambda\kappa}
%%     + E_2 p_{\lambda} p_{\mu} \tilde t^{\lambda\mu\nu}{}^* \tilde a_\nu
%%     \bigg].
%% \end{dmath}
Longitudinal and transverse projectors can be introduced in order to decompose the action and specify in a more standard fashion the dynamics of Eq.~\eqref{4dmax}. This can be done since we have the metric $g_{\mu\nu}$ compatible with the connection, and $\nabla^\mu=g^{\mu\nu}\nabla_\nu$. Additionally we will denote by $\Delta = \nabla^\mu\nabla_\mu$ the covariant Laplacian. Let us define $P_{\texttt{L}}{}^\mu{}_\nu=\nabla^\mu\Delta^{-1} \nabla_\nu $, the projector into logitudinal vectors, and similarly $P_\perp{}^\mu{}_\nu=\delta^\mu_\nu -P_{\texttt{L}}{}^\mu{}_\nu$ is the projector into transverse vectors. Therefore, transverse indices are defined such that $\nabla_\mu A_\perp{}^{\mu}=0$.

Thus, the perturbations can be split into their longitudinal and transverse components as
\begin{dmath}
  a_\mu = {a_\perp}_{\mu} + {\nabla}_{\mu}{aL},
\end{dmath}
\begin{dmath}
  {t}^{\lambda \mu \nu} =
  {t_\perp}^{\lambda \mu \nu}
  + 2  {\nabla}^{\lambda} {t_{\texttt{a}}^{\mu \nu}}
  - 2  {\nabla}^{[\mu}{{t_{\texttt{a}}}^{\nu] \lambda}} 
  + 2  {\nabla}^{\mu}{{t_{\texttt{s}}}^{\nu \lambda}}
  + 2  {\nabla}^{\lambda [\mu}{{t_{\texttt{v}}}^{\nu]}}
\end{dmath}
and
\begin{dmath}
  {\gamma}^{\lambda}\,_{\mu \nu}  =
  {\gamma_\perp}^{\lambda}{}_{\mu \nu}
  + {\nabla}^{\lambda}{{\gamma_{\texttt{s}}}_{\mu \nu}}
  + 2  {\nabla}_{(\mu}{{\gamma}^{\lambda}\,_{\nu)}}
  + 2  {\nabla}^{\lambda}\nabla_{(\mu}{{\gamma_{\texttt{v}}}_{\nu)}}
  + 2  \nab{(\mu} \nab{\nu)} {{\gamma_{\texttt{v}'}}^{\lambda}} 
  + 2  {\nabla}^{\lambda}\nab{(\mu} \nab{\nu)}{\gamma_{\texttt{L}}},
\end{dmath}
where all the indices are transverse except those of the derivative $\nabla_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the sub indices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation. In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless. \hl{check the last sentence. Is this ${t_s}^{\alpha}{}_{\alpha}$?... If true, this condition will kill the scalars contribution in the next equations}
  \label{pert-Lambda}

@@

    S = \int \dn{4}{x} \Bigg(
    C_1 \Big( {t_s}^{\alpha\beta }-\frac{1}{4}g^{\alpha\beta}{{t_s}^{\gamma}{}_{\gamma}} \Big) \bigg( -  (\frac{4\Lambda^2}{3}+\Lambda \Delta+\Delta^2) {\gamma_s}_{\alpha\beta}  
    - \frac{8}{3}   \Lambda\Delta {{\gamma}_{\alpha\beta}} 
    \bigg)
    + {{t_v}^{\alpha}}\bigg(
    \Big(( C_1 - 2\, C_2) \Delta^3 + \frac{1}{3}( C_1 + 2C_2 )\Lambda\Delta^2 + \frac{2}{3}( 2C_1 +  C_2 )\Lambda^2\Delta - \frac{1}{3}C_1  \Lambda^3\Big){{\gamma_v}_{\alpha}}
    + \Big((C_1 - 2\, C_2) \Lambda\Delta - 2\, C_2 \Delta^2\Big){{\gamma_\perp}^{\beta}\,_{\beta \alpha}}
    + 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} \Delta{\nabla}^{\beta }\Delta{{t_a}^{\gamma\delta}}  
    +\Big(- 2\, E_2 \Delta^2 +  (- E_2 + B_3 - \frac{2}{3}\, B_4) \Lambda\Delta\Big){a_\perp}_{\alpha} 
    \bigg)
    + {{t_s}^{\alpha}{}_{\alpha}}\bigg( \frac{2}{3}C_1 \Lambda\Delta{{\gamma}^{\beta}\,_{\beta}} 
    + \frac{2}{3}E_2 \Lambda \Delta{a_L}  
    - \frac{4}{3}C_1 \Lambda^2 \Delta{g_L}
    - \frac{1}{4}C_1 (\Lambda + \Delta)  \Delta{{\gamma_s}^{\beta}{}_{\beta}}
    \bigg)   \Bigg),

@@

  \hl{1.- Is it Ok? 2.- Are the $B_3$ and $B_4$ there?}
  where $\Delta \equiv \nabla^{\alpha}\nabla_{\alpha}$ is the Laplacian operator.
  This action sets the dynamics of two transverse-traceless tensors (or specific combination of tensors), as well as two transverse vectors and two scalars.
%% We define the projector into logitudinal vectors $P_{\texttt{L}}{}^\mu_\nu = \tfrac{1}{p^2}p^\mu p_\nu $, with $p^\mu = g^{\mu\nu} p_\nu$, such that $$A_{\texttt{L}\mu} = P_{\texttt{L}}{}^\nu_\mu \, A_\nu = A_{\texttt{L}} \, p_{\mu},$$ where $A_{\texttt{L}}=\tfrac{1}{p^2} p^\mu A_\mu$. Similarly, $P_\perp{}^\mu_\nu=\delta^\mu_\nu -P_{\texttt{L}}{}^\mu_\nu$ defines the projector into transverse vectors, i.e., $A_{\perp \mu}=P_{\perp}{}_\mu^\nu A_\nu$. Thus,
%% \begin{dmath}
%%   \label{transversea}
%%   \tilde a_\nu=a_\perp{}_{\nu}+a_{\texttt{L}} p_\nu,
%% \end{dmath}
%% \begin{dmath}
%%   \label{transverset}
%%   \tilde t^{\lambda\mu\nu}=\frac{1}{p}\epsilon^{\mu\nu\kappa\rho}p_\rho t_\perp^{\lambda}{}_\kappa+\frac{1}{p^2}p^\lambda\epsilon^{\mu\nu\kappa\rho}p_\rho t_{\texttt{a}\kappa}-\frac{2}{p^2}p^{[\mu}\epsilon^{\nu]\lambda\kappa\rho}p_\rho t_{\texttt{a}\kappa}+\frac{2}{p}p^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+\frac{2}{p^2}p^\lambda p^{[\mu} t_{\texttt{v}}^{\nu]},
%% \end{dmath}
%% \begin{dmath}
%%   \label{transversegamma}
%%   \tilde \gamma^{\lambda}{}_{\mu\nu}=\gamma_\perp^{\lambda}{}_{\mu\nu}+\frac{1}{p}p^\lambda \gamma_{\texttt{s}}{}_{\mu\nu}+\frac{2}{p}p_{(\mu} \gamma^\lambda{}_{\nu)}+\frac{2}{p^2}p^\lambda p_{(\mu} \gamma_{\texttt{v}}{}_{\nu)}+ \frac{1}{p^2}p_{\mu} p_{\nu} \gamma'_{\texttt{v}}{}^\lambda+\frac{1}{p^3}p^\lambda p_{\mu} p_{\nu} \gamma_{\texttt{L}},
%% \end{dmath}
%% where all the indices are transverse except those of the momentum $p_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the subindices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation. In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless. Additionally, we could separate the fields into irreducible representations by projecting them into their traceless part and other lower dimensional tensor representations. In the meanwhile we shall not do this expansion.
%% \begin{widetext}
%%   Using Eqs.~\eqref{transversea}, \eqref{transverset} and~\eqref{transversegamma}, the action~\eqref{4dflat} is then rewritten
%%   \begin{dmath}
%%     \label{4dtransverse}
%%     S =
%%     \int\dn{4}{p}p^2
%%     \bigg[
%%       2C_1 \hat{p}_\mu \hat{p}_\sigma\Big(\gamma_\perp^{\mu}{}_{\rho\nu}+\hat{p}^\mu \gamma_{\texttt{s}}{}_{\rho\nu}+2\hat{p}_{(\rho} \gamma^\mu{}_{\nu)}+2\hat{p}^\mu \hat{p}_{(\rho} \gamma_{\texttt{v}}{}_{\nu)}+ \hat{p}_{\rho} \hat{p}_{\nu} \gamma'_{\texttt{v}}{}^\mu+\hat{p}^\mu \hat{p}_{\rho} \hat{p}_{\nu} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\rho\sigma\delta\eta}\hat{p}_\eta t_\perp^{\nu}{}_\delta+\hat{p}^\nu t_{\texttt{a}}^{\rho\sigma}-2\hat{p}^{[\rho} t_{\texttt{a}}^{\sigma]\nu}+2\hat{p}^{[\rho} t_{\texttt{s}}^{\sigma]\nu}+2\hat{p}^\nu \hat{p}^{[\rho} t_{\texttt{v}}^{\sigma]}\Big)
%%       +2C_2 \hat{p}_{\mu} \hat{p}_\sigma\Big(\gamma_\perp^{\rho}{}_{\nu\rho}+\hat{p}^\rho \gamma_{\texttt{s}}{}_{\nu\rho}+2\hat{p}_{(\nu} \gamma^\rho{}_{\rho)}+2\hat{p}^\rho \hat{p}_{(\nu} \gamma_{\texttt{v}}{}_{\rho)}+\hat{p}_{\nu} \hat{p}_{\rho} \gamma'_{\texttt{v}}{}^\rho +\hat{p}^\rho \hat{p}_{\nu} \hat{p}_{\rho} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\kappa+\hat{p}^\sigma t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\sigma}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\sigma}+2\hat{p}^\sigma \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)
%%       +E_1 \hat{p}_{\rho} \hat{p}_{\sigma}\Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\rho}{}_\kappa+\hat{p}^\rho t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{\mu} t_{\texttt{a}}^{\nu\rho}+2\hat{p}^{\mu} t_{\texttt{s}}^{\nu\rho}+2\hat{p}^\rho \hat{p}^{\mu} t_{\texttt{v}}^{\nu}\Big)^*\Big(\epsilon^{\lambda\kappa\delta\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\delta+\hat{p}^\sigma t_{\texttt{a}}^{\lambda\kappa}-2\hat{p}^{\lambda} t_{\texttt{a}}^{\kappa\sigma}+2\hat{p}^{\lambda} t_{\texttt{s}}^{\kappa\sigma}+2\hat{p}^\sigma \hat{p}^{\lambda} t_{\texttt{v}}^{\kappa}\Big)\epsilon_{\mu\nu\lambda\kappa}
%%       +E_2 \hat{p}_{\lambda} \hat{p}_{\mu} \Big(\epsilon^{\mu\nu\kappa\rho}\hat{p}_\rho t_\perp^{\lambda}{}_\kappa+\hat{p}^\lambda t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\lambda}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+2\hat{p}^\lambda \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)^*\Big(a_\perp{}_\nu+\hat{p}_\nu a_{\texttt{L}}\Big)
%%       \bigg],
%%   \end{dmath}
%% \end{widetext}
%% simplifiying
%% \begin{dmath}
%%   \label{WithGhosts}
%%   S=\int d^4p\Bigg[-2C_1 p^2\gamma_{\texttt{s}\mu\nu}^*t_{\texttt{s}}^{\mu\nu}
%%     +p^2\Big((-2C_1+2C_2)\gamma_{\texttt{v}\mu}+2C_2\gamma_{\perp\mu\nu}^\nu
%%     +8E_1t_{\texttt{a}\mu}+E_2a_{\perp\mu}\Big)^*t_{\texttt{v}}^\mu
%%     \Bigg]
%% \end{dmath}
When we restrict ourselves to perturbations around a flat (Minkowski) spacetime, the above equation simplifies greatly,

@@

  S = \int \dn{4}{x} \, \bigg[
    - C_1 ( \Delta\gamma_{\texttt{s}\mu\nu})^* \Delta t_{\texttt{s}}^{\mu\nu}
    + \Big( ( C_1 - 2 C_2) \nabla^\nu \Delta \nabla_\nu \gamma_{\texttt{v}\mu}
    - 2 C_2 \Delta \gamma^\nu_{\perp\nu\mu}
    - 8 E_1 \epsilon_{\alpha\beta\nu\mu} \nabla^{\alpha} \Delta t_{\texttt{a}}^{\beta\nu}
    - 2 E_2 \Delta a_{\perp\mu} \Big)^* \Delta t_{\texttt{v}}^\mu

@@

\hl{Where are the scalars? This has 18 dof, while the previous one has 20 dof. According to the counting, there are 18... I suppose that eighteen is the correct answer, but What is wrong in the first expression?} and it is clear that there are only eighteen degrees of freedom, corresponding to a couple of transverse-traceless rank-two-tensors, and a couple of transverse vectors.

We have checked, using the method introduced in Ref.~\cite{Diaz:2014yua}, that the formal counting of degrees of freedom for the effective action in Eq.~\eqref{eff-action} yields eighteen degrees of freedom. We discover during the implementation of these program, that our model presents an extra symmetry associated to the metric independence property.

@@

In this paper we have shown that the \emph{polynomial affine gravity} presented in Ref.~\cite{Skirzewski:2014eta} is the most general (polynomial) model for an affine theory of gravity, see the Appendix~\ref{sec:ld}, consistent with invariance under diffeomorphisms. The action in Eq.~\eqref{4dfull}, is parametrized by a nineteen-dimensional moduli space---after the boundary and topological terms have been dropped---, which in some sense made us wonder about a possible \emph{duality} between this model and the one proposed in Ref.~\cite{Pagani:2015ema}, even though the last one possesses a metric field.
%% (boundary condition, topological terms, ...)
